### 2017-03-31 paper/modes.tex
pass on section 2

This section provides important background on parallel test execution.

Parallelism in test execution can be obtained at different levels.
Figure~\ref{fig:levels} illustrates these levels.  The highest
level indicates parallelism that can be obtained through different
machines on the network.  For instance, using virtual machines from a
cloud service to perform a distributed execution.  The machine space
sits under the ``network space'' and provides a \emph{lower-level}
parallelism.  In this case, computation can be offloaded at different
CPUs within a machine and at different threads within each CPU.  Note
that all these levels are complementary:  low-level parallelization
schemes could leverage the computing power of server nodes in addition
to the aggregate processing power of the farm.

This paper focuses at low-level parallelism (\ie, machine and CPU
space), which can be enabled through build systems and testing
frameworks.  Given the proliferation of multi-core machines it is not
surprising that testing frameworks provide today support for parallel
test execution (e.g., JUnit~\cite{junit-org}, TestNG~\cite{testng},
and NUnit~\cite{nunit}).  In the following we elaborate relevant
features of and testing frameworks build systems.  We focused on Java,
Maven, and JUnit but the discussion can be generalized to other
language and tools.

@@

>>>>

Parallelism in test execution can be obtained at different levels.
Figure~\ref{fig:levels} illustrates this.  The highest level indicates
parallelism that can be obtained through different machines on the
network.  For instance, using virtual machines from a cloud service to
distribute test execution.  The lowest levels denote parallelism
obtained within a single machine.  These levels are complementary:
low-level parallelization leverages the computing power of server
nodes whereas high-level schemes leverage the aggregate processing
power of the farm.

This paper focuses at low-level parallelism, where computation can be
offloaded at different CPUs within a machine and at different threads
within each CPU.  This form of parallelism is enabled through build
systems (spawning processes in different CPUs) and testing frameworks
(spawning threads in a CPU).  It is important to note that a variety
of testing frameworks provide today support for parallel test
execution (e.g., JUnit~\cite{junit-org}, TestNG~\cite{testng}, and
NUnit~\cite{nunit}) as to leverage the power of multi-core processors.
In the following, we elaborate relevant features of testing frameworks
and build systems.  We focused on Java, Maven, and JUnit but the
discussion can be generalized to other language and tools.

@@

%%  LocalWords:  parallelization CPUs JUnit TestNG NUnit multi JVM de
%%  LocalWords:  JVMs falar explicar configuracao ilustrada levanta
%%  LocalWords:  uma por cria cada executar paralelo escapeinside
